Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
Typo.

\section{UX sprint}
\label{sec:pilot}
\indent \indent This pilot was to test-drive an experiment which examines the usability of Tor as an anonymity tool
with respect to a target demographic of users known to use Tor (journalists who have reported in other
countries). We emphasized the targeting of a high-risk user group of Tor and to 
target usability changes aimed at helping those who could not afford to make mistakes. To see 
if those users had any potentially damaging misunderstandings or incomprehensions of Tor, 
we created tasks to licit Tor's non-typical behaviors and ask our participants to
navigate through more advanced settings.

>>>>

\section{UX sprint}
\label{sec:pilot}
\indent \indent This pilot was to test-drive an experiment which examines the usability of Tor as an anonymity tool
with respect to a target demographic of users known to use Tor (journalists who have reported in other
countries). We emphasized the targeting of a high-risk user group of Tor and to 
target usability changes aimed at helping those who could not afford to make mistakes. To see 
if those users had any potentially damaging misunderstandings or incomprehensions of Tor, 
we created tasks to elicit Tor's non-typical behaviors and ask our participants to
navigate through more advanced settings.
